Title

### 2017-03-25 paper.tex
Update the numbers

    Our experiment begins with known tuning practices which includes processor isolation \cite{isolatedcpu}, tickless
    feature of kernel \cite{tickless}, L2 cache lockdown. We compared the measurement result of mctest with and without
    these tuning techniques on Freesacle i.mx6 Sabre platform. Measurement results are shown in figure
    \ref{fig:imx6_mctest_v}, \ref{fig:imx6_mctest_iso}, and \ref{fig:imx6_mctest_lock}, verifying the effectiveness of
    these known tuning techniques and providing results as a baseline. We are able to see the WECT with and without
    tuning are 100us and 100us. This gives us the hint that the scheduling would harms the real-time performance. This
    scheduling overhead could be separated into 2 parts, scheduler overhead and cache contention on SMP system. With L2
    Cache lockdown technique we are able to mitigate most of the cache contention, but still resulting some degree of
    jitter about 100us

@@

    In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WECT of 50us and 50us. With these result, we are
    able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time
    applications as kernel modules. But this is tedious and making the debugging process difficult. Thus, we proposed a
    second approach, Kernel Mode Linux(KML) \cite{KML} \cite{KMLConf}. KML enables the ability for specified user-space
    program running in kernel memory space. Thus, system calls become jump instructions, not instruction trapping the
    processor. Also, this would mitigate the cache contention while switching in and out the kernel during system call.
    In addition, we have also rewired system calls, which have vDSO implementations \cite{vDSO}, to use vDSO
    implementation via KML. The result of user-space program running in KML is shown in figure \ref{fig:imx6_mctest_kml}
    with WECT of 20us, which proving the effectiveness of jitter mitigation from KML.

@@

    Identifying that scheduler is also a source of jitter, we applied our proposed scheduler profiling tool to evaluate
    and identify of which part of the scheduling process is the source of jitter. Knowing the IRQ latency, and
    context-switching latency, we would like to evaluate the scheduler duration. Traditionally, the latency of this part
    is considered static with the CFS algorithm complexity, designed to be O(1), but real measurement result are
    lacking. Thus, we set our proposed profiler to record the increment of scheduler run-queue and scheduler
    context-switching events with switched-to PID of each processors. A analyzer will process the recorded data and
    gives out the scheduler duration of a specified process, enabling us the understand the scheduling of real-time task
    in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure
    \ref{fig:sd_solo}. The latency could be considered static with maximum 10us. This result matches traditional
    considerations, but with the interference from other work-load, the jitter will start to emerge.

@@

    We created additional work-load, executing alone with cyclictest during profiling session. We created a mild loading
    condition, which has 3 stress threads, and a heavy loading condition, which has 8 stress threads. The result of mild
    loading condition is shown in figure \label{fig:sd_mild}. This result also exhibits a mostly static scheduler
    duration with seldom jitter with maximum of 20us. But putting the system in to heavy loading condition, the result,
    shown in figure \ref{fig:sd_heavy} exhibits random jitter from 10us to 30us. The spread of distribution of scheduler
    duration, shown in figure \ref{fig:sd_heavy_d}, would become wilder. This informs us that the scheduler duration is
    not a static value and will increase alone with the system's load. Also informs that the scheduler duration contains
    but not only contains CFS algorithm task selection process which is proved to be O(1).

@@

    We also captured large jitter of scheduler duration on a mild loaded system. The experiment is running mctest with
    cyclictest. We pinned kernel module mctest to use first processor, causing cyclictest real-time thread and main
    thread being scheduler onto second processor. On most of the time, this execution schema results the same result as
    cyclictest executing solely in the system. But on some occasions, the cyclictest main thread would be waken-up and
    enter run-queue with short inter-arrival time against the cyclictest real-time thread, which was also being
    waken-up. When this event happened, the scheduler duration will raise to 30us. This result, shown in figure
    \ref{fig:sd_mctest} hints us that not only long term overload system would exhibit large scheduler duration, but
    also short burst a overloading condition during the real-time task scheduling and execution would cause the
    scheduler duration to raise.

>>>>

    Our experiment begins with known tuning practices which includes processor isolation \cite{isolatedcpu}, tickless
    feature of kernel \cite{tickless}, L2 cache lockdown. We compared the measurement result of mctest with and without
    these tuning techniques on Freesacle i.mx6 Sabre platform. Measurement results are shown in figure
    \ref{fig:imx6_mctest_v}, \ref{fig:imx6_mctest_iso}, and \ref{fig:imx6_mctest_lock}, verifying the effectiveness of
    these known tuning techniques and providing results as a baseline. We are able to see the WECT with and without
    tuning are 153us and 86us. This gives us the hint that the scheduling would harms the real-time performance. This
    scheduling overhead could be separated into 2 parts, scheduler overhead and cache contention on SMP system. With L2
    Cache lockdown technique we are able to mitigate most of the cache contention, but still resulting some degree of
    jitter about 76us in maximum.

@@

    In addition, we compared the user-space mctest result with kernel space measurement, shown in figure
    \ref{fig:imx6_mctest_k_v} and \ref{fig:imx6_mctest_k_lock} with WECT of 27us and 17us. With these result, we are
    able to identify the sources of jitter are system calls. To mitigate these, we first proposed to rewrite real-time
    applications as kernel modules. But this is tedious and making the debugging process difficult. Thus, we proposed a
    second approach, Kernel Mode Linux(KML) \cite{KML} \cite{KMLConf}. KML enables the ability for specified user-space
    program running in kernel memory space. Thus, system calls become jump instructions, not instruction trapping the
    processor. Also, this would mitigate the cache contention while switching in and out the kernel during system call.
    In addition, we have also rewired system calls, which have vDSO implementations \cite{vDSO}, to use vDSO
    implementation via KML. The result of user-space program running in KML is shown in figure \ref{fig:imx6_mctest_kml}
    with WECT of 27us (excluding initialization jitter), which proving the effectiveness of jitter mitigation from KML.

@@

    Identifying that scheduler is also a source of jitter, we applied our proposed scheduler profiling tool to evaluate
    and identify of which part of the scheduling process is the source of jitter. Knowing the IRQ latency, and
    context-switching latency, we would like to evaluate the scheduler duration. Traditionally, the latency of this part
    is considered static with the CFS algorithm complexity, designed to be O(1), but real measurement result are
    lacking. Thus, we set our proposed profiler to record the increment of scheduler run-queue and scheduler
    context-switching events with switched-to PID of each processors. A analyzer will process the recorded data and
    gives out the scheduler duration of a specified process, enabling us the understand the scheduling of real-time task
    in SMP system. The result of running a solo instance of cyclictest on SoC FPGA Development Kit is shown in figure
    \ref{fig:sd_solo}. The latency could be considered static with maximum 17us. This result matches traditional
    considerations, but with the interference from other work-load, the jitter will start to emerge.

@@

    We created additional work-load, executing alone with cyclictest during profiling session. We created a mild loading
    condition, which has 3 stress threads, and a heavy loading condition, which has 8 stress threads. The result of mild
    loading condition is shown in figure \label{fig:sd_mild}. This result also exhibits a mostly static scheduler
    duration with seldom jitter with maximum of 20us. But putting the system in to heavy loading condition, the result,
    shown in figure \ref{fig:sd_heavy} exhibits random jitter up to 34us. The spread of distribution of scheduler
    duration, shown in figure \ref{fig:sd_heavy_d}, would become wilder. This informs us that the scheduler duration is
    not a static value and will increase alone with the system's load. Also informs that the scheduler duration contains
    but not only contains CFS algorithm task selection process which is proved to be O(1).

@@

    We also captured large jitter of scheduler duration on a mild loaded system. The experiment is running mctest with
    cyclictest. We pinned kernel module mctest to use first processor, causing cyclictest real-time thread and main
    thread being scheduler onto second processor. On most of the time, this execution schema results the same result as
    cyclictest executing solely in the system. But on some occasions, the cyclictest main thread would be waken-up and
    enter run-queue with short inter-arrival time against the cyclictest real-time thread, which was also being
    waken-up. When this event happened, the scheduler duration will raise to maximum of 23us. This result, shown in
    figure \ref{fig:sd_mctest} hints us that not only long term overload system would exhibit large scheduler duration,
    but also short burst a overloading condition during the real-time task scheduling and execution would cause the
    scheduler duration to raise.
